Modelling potential environmental impacts of science activity in Antarctica

### 2025-06-25 paper/paper.qmd
fixed waited/weighted typo

This is relatively straightforward and like radius limited betweenness involves limiting the shortest paths considered to only those among a chosen subset of vertices in the graph.
One slight simplification we make for performance reasons is to weight every appearance of a vertex on a geodesic as equal, even if multiple equal length shortest paths exist between two vertices. 
In practice, this is unlikely to have much effect on the resulting estimates of relative betweenness, since with real-valued edge costs two paths of exactly equal cost are unlikely.
An example result is shown in @fig-betweenness-limited-sites.
One refinement shown in the figure is that sites have been waited by relative importance so that a site such as an expedition base camp can be expected to originate more trips than other sites.

>>>>

This is relatively straightforward and like radius limited betweenness involves limiting the shortest paths considered to only those among a chosen subset of vertices in the graph.
One slight simplification we make for performance reasons is to weight every appearance of a vertex on a geodesic as equal, even if multiple equal length shortest paths exist between two vertices. 
In practice, this is unlikely to have much effect on the resulting estimates of relative betweenness, since with real-valued edge costs two paths of exactly equal cost are unlikely.
An example result is shown in @fig-betweenness-limited-sites.
One refinement shown in the figure is that sites have been weighted by relative importance so that a site such as an expedition base camp can be expected to originate more trips than other sites.
